### 2014-05-21 intro.tex
Revise

>>>>

More broadly, automated protocol-design tools have led us to a style
of design where the value of information can be evaluated
empirically. We may give Remy access to a new congestion
signal---either a function of existing TCP acknowledgments from the
receiver, or based on a new source of information---and measure
how much the resulting congestion-control algorithm improves over the
status quo. Similarly, we can knock out an existing signal and rerun
Remy to measure how much the loss would hurt performance.

After investigating many candidate signals, we have ended up with
computer-generated algorithms that collect four congestion signals
(Section~\ref{ss:signals}). \textbf{None of these signals} is
collected by existing TCP congestion-control schemes. Our
simulation experiments indicate each signal is individually valuable on
top of the other three.

\subsection{Windowing and pacing work well together}
